linguistic_analysis_C-D.Rmd : Linguistic quantity and complexity

### 2021-07-21 code/linguistic_analysis_C-D.Rmd
add feedback code

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(here)
library("stringr")
```

@@

```{r main data, include=TRUE}
data_target = "pilot0"
data_location=paste0("data/",data_target)

d_flowers<- read_csv(here(data_location, "raw_chat.csv"))%>%
 filter(!is.na(text))

@@

ggplot(d_flowers_utt_length, aes(x=repNum, y=total_num_words, color=as.factor(playerId)))+
  scale_color_brewer(palette="Dark2")+
  facet_grid(cols = vars(blockNum), rows =vars(gameId)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  scale_y_continuous(limits = c(0,50))+
  labs(title="Number of words", y="Total number of words", x="Round number", color="playerId")+
  theme(legend.position="bottom") + 
  theme_bw()

ggplot(d_flowers_utt_length, aes(x=repNum, y=mlu, color=as.factor(playerId)))+
  scale_color_brewer(palette="Dark2")+
  facet_grid(cols = vars(blockNum), rows =vars(gameId)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  scale_y_continuous(limits = c(0,15))+
  labs(title="MLU", y="MLU", x="Round number", color="playerId")+
  theme(legend.position="bottom") + 
  theme_bw()

@@

ggplot(d_flowers_n_turns, aes(x=trialNum, y=n, color=as.factor(playerId)))+
  facet_grid(rows =vars(gameId)) +
  scale_color_brewer(palette="Dark2")+
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of turns", y="Number of turns", x="Round number", color="playerId")+
  theme(legend.position="bottom") + 
  theme_bw()

@@

ggplot(d_flowers_n_utt_speaker, 
       aes(x=trialNum, y=n_utt_speaker, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_grid(~playerId) +
  xlab("Round number") + 
  ylab("Number of turns") + 
  theme_bw()
```

@@

library("spacyr")

@@

ggplot(d_flowers_ttr, 
       aes(x=trialNum, y=ttr_, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_grid(rows =vars(gameId)) +
  xlab("Round number") + 
  ylab("Type_token ratio") + 
  theme_bw()

@@

ggplot(d_flowers_n_utt_dist, 
       aes(x=trialNum, y=overall_turns, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_wrap(~playerId)+
  xlab("Round number") + 
  ylab("Proportion of turns") + 
  theme_bw()

@@

```{r cars}

@@

ggplot(d_flowers_q, 
       aes(x=trialNum, y=prop_questions, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  facet_wrap(~ playerId) +
  geom_point(alpha=.1) +
  xlab("Round number") + 
  ylab("Proportion of questions") + 
  theme_bw()

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(here)
library("stringr")
library(Hmisc)
library("spacyr")
library(ggrepel)

@@

```{r main data, include=TRUE}
d<- read_csv("~/Downloads/raw_chat.csv")
d <- d %>% filter(type=="message")
write_csv(d, "~/Downloads/raw_chat1.csv")
```

```{r main data1, include=TRUE}
data_target = "pilot0"
data_location=paste0("data/",data_target)

d_flowers<- read_csv(here(data_location, "raw_chat1.csv"))%>%
 filter(!is.na(text))

@@

ggplot(d_flowers_utt_length, aes(x=repNum, y=total_num_words, color=as.factor(playerId)))+
  scale_color_brewer(palette="Dark2")+
  facet_grid(cols = vars(blockNum), rows =vars(gameId)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  scale_y_continuous(limits = c(0,50))+
  labs(title="Number of words", y="Total number of words", x="Round number", color="playerId")+
  theme(legend.position="bottom") + 
  theme_bw() +
  ggtitle("Number of words per Round")

ggplot(d_flowers_utt_length, aes(x=repNum, y=mlu, color=as.factor(playerId)))+
  scale_color_brewer(palette="Dark2")+
  facet_grid(cols = vars(blockNum), rows =vars(gameId)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  scale_y_continuous(limits = c(0,15))+
  labs(title="MLU", y="MLU", x="Round number", color="playerId")+
  theme(legend.position="bottom") + 
  theme_bw()+
  ggtitle("MLU per Round")

@@

ggplot(d_flowers_n_turns, aes(x=trialNum, y=n, color=as.factor(playerId)))+
  facet_grid(rows =vars(gameId)) +
  scale_color_brewer(palette="Dark2")+
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of turns", y="Number of turns", x="Round number", color="playerId")+
  theme(legend.position="bottom") + 
  theme_bw() +
  ggtitle("Number of turns per Round")

@@

ggplot(d_flowers_n_utt_speaker, 
       aes(x=trialNum, y=n_utt_speaker, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_grid(~playerId) +
  xlab("Round number") + 
  ylab("Number of utterances") + 
  theme_bw()

@@

@@

ggplot(d_flowers_ttr, 
       aes(x=trialNum, y=ttr_, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_grid(rows =vars(gameId)) +
  xlab("Round number") + 
  ylab("Type_token ratio") + 
  theme_bw()+
  ggtitle("TTR per Round")

@@

ggplot(d_flowers_n_utt_dist, 
       aes(x=trialNum, y=overall_turns, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_wrap(~playerId)+
  xlab("Round number") + 
  ylab("Proportion of turns") + 
  theme_bw()+
  ggtitle("Proportion of turns per Round")

@@

```{r questions}

@@

ggplot(d_flowers_q, 
       aes(x=trialNum, y=prop_questions, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  facet_wrap(~ playerId) +
  geom_point(alpha=.1) +
  xlab("Round number") + 
  ylab("Proportion of questions") + 
  theme_bw()+
  ggtitle("Proportion of questions per Round")

@@

### 1. Distribution of speech across speakers
```{r feedback}

###politeness markers

###backchanneling: (https://www.reading.ac.uk/AcaDepts/ll/app_ling/internal/Cutrone_vol_2.pdf)

backchanneling<- c("mm", "okay", "uh-huh", "ok", "mm-hm", "uh", "um", "agree", "uhuh", "mmm", "wow", "great", "mm", "hm",  "ummm", "hmmmm", "huh", "un", "um", "ohh", "ooo", "see", "oooo", "ununun", "oh", "ah", "true", "agree", "right", "yeah", "good", "really")

###hedges: (https://www.researchgate.net/publication/280125979_Linguistic_Markers_and_Stylistic_Attributes_of_Hedging_in_English_Academic_Papers_Written_by_Native_and_Non-Native_Speakers_of_English/figures)

hedging <- c("may", "perhaps", "might", "possible", "likely", "possibly", "maybe", "probable", "appear", "seem", "suggest", "sometimes", "seemingly", "apparently", "often", "could", "usually", "likely", "tend", "sometimes", "probably", "primarily", "tendency", "largely")

d_flowers_feedback <- d_flowers %>%
  group_by(playerId, trialNum, gameId, blockNum) %>%
  mutate(text = gsub('[[:punct:] ]+',' ',text)) %>%
  mutate(text = strsplit(text, " ")) %>%
  rowwise() %>%
  mutate(backchannel=list(intersect(backchanneling, text))) %>%
  mutate(backchannel_length=length(backchannel))%>%
  mutate(hedge=list(intersect(hedging, text))) %>%
  mutate(hedge_length=length(hedge))

ggplot(d_flowers_feedback, aes(y=trialNum , x=backchannel_length, label=playerId)) +
  facet_wrap(~ playerId) +
  geom_bar(stat="identity")

ggplot(d_flowers_feedback, aes(y=trialNum , x=hedge_length, label=playerId)) +
  facet_wrap(~ playerId) +
  geom_bar(stat="identity")

ggplot(d_flowers_feedback, aes(y=trialNum , x=backchannel_length, label=playerId)) +
  geom_point(alpha = .5)+
  geom_smooth() +
  geom_text_repel(aes(label=ifelse(backchannel=="character(0)",  "", backchannel), max.overlaps = 20))+
  xlim(c(1,5))+
  theme_bw()

ggplot(d_flowers_feedback, aes(y=trialNum , x=hedge_length, label=playerId)) +
  geom_point(alpha = .5)+
  geom_smooth() +
  geom_text_repel(aes(label=ifelse(hedge=="character(0)", "", hedge), max.overlaps = 20))+
  xlim(c(1,5))+
  theme_bw()

```{r minimum_edit_distance, include=TRUE}
